Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-19 paper.tex
improving (making clear) some sentences

The problem to solve in this work is the forecasting of sales for new launched books in the Spanish market, considering a set of `pre-sales variables'.
The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book which before its publication process starts. This is a forecasting problem for which no specific historical data are available, since the same book has not been previously published.
However, we have considered data about other previously published books and have taken as reference a set of variables (or features), related with the book publication process.

>>>>

The problem to solve in this work is the forecasting of sales for new launched books in the Spanish market, considering a set of `pre-sales variables'.
The objective is to offer a tool for publishers which will aid them to decide the best print run for a new book before its publication process starts. This is a forecasting problem for which no specific historical data are available, since the same book has not been previously published.
However, we have considered data about other previously published books and have taken as reference a set of variables (or features), related with the book publication process.
